Concurrent and Distributed Programming in Harmony

### 2022-01-11 paper/paper.tex
Latest

Harmony is heavily based on Python to reduce the learning curve
for users.  Many of Python's powerful constructs and operators are
supported are supported, including comprehensions.  Harmony does
not support classes, and instead supports memory allocation and
pointers in a way that is familiar to C programmers.  While this
seems like a step back in language evolution, many synchronization
algorithms in the literature explicitly consider memory accesses,
and perhaps surprisingly this has been a bonus for analyzing
such algorithms with Harmony.  Moreover, the Harmony model checker 
can be used to check for memory leaks or access to dangling pointers.

@@

While Harmony has proven itself to be effective and even fun to use
for a large variety of synchronization problems and distributed
algorithms, it is not a panacea.  At the core of Harmony is a model
checker and with all its optimizations it can still easily suffer
from combinatorial state explosion in programs that have too many
threads or too many non-deterministic choices.  Nonetheless, because
of its systematic state exploration, many problems can often be
uncovered in small scenarios with few threads and few choices.

@@

>>>>

Harmony is heavily based on Python to reduce the learning curve for
users.  Many of Python's powerful constructs and operators are
supported are supported, including comprehensions.  Harmony does
not support classes, and instead supports memory allocation and
pointers in a way that is familiar to C programmers.  While this
perhaps seems like a step back in language evolution, many
synchronization algorithms in the literature explicitly consider
memory accesses, and perhaps surprisingly this has been a bonus for
analyzing such algorithms with Harmony.  Moreover, the Harmony model
checker can be used to check for memory leaks or access to dangling
pointers.

@@

While Harmony has proven itself to be effective and even fun to use
for a large variety of synchronization problems and distributed
algorithms, it is not a panacea.  At the core of Harmony is a model
checker and---even with all its optimizations---it can still suffer
from combinatorial state explosion in programs that have too many
threads or too many non-deterministic choices.  Nonetheless, because
of its systematic state exploration, many problems can often be
uncovered in small scenarios with few threads and few choices.
Harmony's support for anonymous threads is useful for scaling when
there are many similar threads that do not need to know their own
identifier.  Also, Harmony's support for modular model checking
allows larger systems to be built from smaller ones.

@@

\section{Related Work}

Harmony does not offer much innovation on the front of model checking

PlusCal and TLA+, Promela and Spin, DSLABS (UW), Java Pathfinder, Zing,
CBMC/JBMC.
